\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning up

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Formulation}\label{section:NumericalFormulation}
The method presented here builds on that reported by \citet{jackson_2015} is known as OCVFEM formulation. The method developed is applicable to $N_{p}$ fluid phases and to the general family of $P_{n+1}(DG)-P_{n}(DG)$ element pair consistent dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces. These element-pairs have a discontinuous $n^{th}$-order polynomial representation for velocity and a continuous representation of pressure. The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries (fig.\ref{fig:fem_elem})  , which are limited to yield bounded fields.

@@

Starting from a simple case as this is described in fig. \ref{fig:1}, there is a simple square shape formation consisted of 2 values of different (K) permeabilities. The domain is fully saturated with fluid $2$. We inject fluid $1$ across the left hand side of the formation and we are trying to displace the existing fluid $2$. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$ and a main finger starts to appear.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Numerical Formulation}\label{section:NumericalFormulation}
The method presented here builds on that reported by \citet{jackson_2015, salinas2015} is known as OCVFEM formulation. The method developed is applicable to $N_{p}$ fluid phases and to the general family of $P_{n+1}(DG)-P_{n}(DG)$ element pair consistent dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces. These element-pairs have a discontinuous $n^{th}$-order polynomial representation for velocity and a continuous representation of pressure. The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries (fig.\ref{fig:fem_elem})  , which are limited to yield bounded fields.

@@

Starting from a simple case as this is described in fig. \ref{fig:square}, there is a simple square shape formation consisted of 2 values of different (K) permeabilities (blue and red shaded square areas). The domain is fully saturated with fluid $2$. We inject fluid $1$ across the left hand side of the formation and we are trying to displace the existing fluid $2$. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$ and a main finger starts to appear.
